Ускорение метода глобальной оптимизации за счет выделения локальных экстремумов на основе машинного обучения

### 2021-08-12 2021/Entropy/entropy.tex
добавил третьего автора

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-5273-2471} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0002-8736-0652} % Add \orcidB{} behind the author's name
%\newcommand{\orcidauthorC}{0000-0002-4013-2329} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Konstantin Barkalov $^{1}$*\orcidA{} and Ilya Lebedev $^{1}$\orcidB{}}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Konstantin Barkalov and Ilya Lebedev}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Barkalov, K.; Lebedev, I.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address[1]{%
$^{1}$ \quad Department of Mathematical Software and Supercomputing Technologies, Lobachevsky University, 603950 Nizhni Novgorod, Russia; ilya.lebedev@itmm.unn.ru (I.L.)}
%$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Conceptualization and methodology, K.B.; software and validation, I.L.; formal analysis, K.B.; investigation, I.L.; data curation, I.L.; writing---original draft preparation, K.B.; writing---review and editing, K.B.; visualization, I.L.; funding acquisition, K.B. All authors have read and agreed to the published version of the manuscript.}

>>>>

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-5273-2471} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0002-8736-0652} % Add \orcidB{} behind the author's name
\newcommand{\orcidauthorC}{0000-0001-6776-0096} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Konstantin Barkalov $^{1}$*\orcidA{}, Ilya Lebedev $^{1}$\orcidB{} and Evgeny Kozinov $^{1}$\orcidC{}}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Konstantin Barkalov, Ilya Lebedev and Evgeny Kozinov}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Barkalov, K.; Lebedev, I.; Kozinov, E.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address[1]{%
$^{1}$ \quad Department of Mathematical Software and Supercomputing Technologies, Lobachevsky University, 603950 Nizhni Novgorod, Russia; ilya.lebedev@itmm.unn.ru (I.L.), evgeny.kozinov@itmm.unn.ru (E.A.)}
%$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Conceptualization and methodology, K.B.; software and validation, I.L., E.A.; formal analysis, K.B.; investigation, I.L.; data curation, I.L.; writing---original draft preparation, K.B.; writing---review and editing, K.B.; visualization, I.L.; funding acquisition, K.B. All authors have read and agreed to the published version of the manuscript.}
